---
title: "Working with Data in Tidyverse"
author: "Ichsan"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    code_folding : hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    number_sections: true
---

<style>
#TOC {
  color: #708090;
  font-family: Calibri;
  font-size: 16px; 
  border-color: #708090;
}
body {
  color: #708090;
  font-family: Calibri;
  background-color: #ffffff;
}
pre {
  color: #708090;
  background-color: #F8F8FF;
}
h1.title {
  color: #0e2d4d;
  font-family: Calibri;
}
h4.date {
  color: #708090;  
  font-family: Calibri;
}
</style>


```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.align = 'center', echo = TRUE)
```

```{r load package, message = FALSE, warning = FALSE}
library(tidyverse)
library(skimr)
library(kableExtra)
```

# Step One

## Load data
```{r data, warning = FALSE, message = FALSE}
raw_data <- read_csv("bq-results-20210310-090242-q2qxhktlxsw9.csv",
         na = c("", "NA", "N/A"),
         col_types = cols(
         content_groups = col_factor(levels = NULL)
           )
         )
group_data <- read_csv("raw_avid_content_groups.csv",
                       na = c("", "NA", "N/A"),
                       col_types = cols(
                       content_groups = col_factor(levels = NULL)
                       )
                      )

glimpse(raw_data)

unique(raw_data$content_groups)

glimpse(group_data)

unique(group_data$array_cg)


```

# EDA

## Cek Grouping content_group and title

### Top 20 TV Contents content_groups
```{r out.width='65%'}
raw_data %>%
  filter(content_groups %in% c('TV Contents')) %>%
  select(content_groups,title,watchers_this_mtd,watchers_prev_mtd) %>% 
  arrange(desc(watchers_this_mtd)) %>%
  head(20) %>%
  kbl() %>%
  kable_paper("hover", full_width = F)
```

### Top 20 General Entertainment content_groups
```{r}
raw_data %>%
  filter(content_groups %in% c('General Entertainment')) %>%
  select(content_groups,title,watchers_this_mtd,watchers_prev_mtd) %>% 
  arrange(desc(watchers_this_mtd)) %>%
  head(20) %>%
  kbl() %>%
  kable_paper("hover", full_width = F)
```

### Top 20 Films content_groups
```{r}
raw_data %>%
  filter(content_groups %in% c('Films')) %>% 
  select(content_groups,title,watchers_this_mtd,watchers_prev_mtd) %>% 
  arrange(desc(watchers_this_mtd)) %>%
  head(20) %>%
  kbl() %>%
  kable_paper("hover", full_width = F)
```

### Top 50 "General Entertainment,TV Contents"
```{r warning = F}
group_data %>%
  filter(array_cg %in% c("General Entertainment,TV Contents")) %>%
  select(content_groups,title,total_watchers,total_events) %>%
  arrange(desc(total_watchers)) %>%
  head(50) %>%
  kbl() %>% 
  #column_spec(1, background = ifelse(group_data$content_groups == "General Entertainment", "yellow", "white")) %>%
  kable_paper("hover", full_width = F) %>% 
  kable_styling(fixed_thead = T, font_size = 7)
```



