---
title: "Investment Report for Projects in `r params$country`"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    code_folding : hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    number_sections: true
params:
  country: Brazil
  year_start: 2017-07-01
  year_end: 2018-06-30
  fy: 2018    
---
<style>
#TOC {
  color: #708090;
  font-family: Calibri;
  font-size: 16px; 
  border-color: #708090;
}
body {
  color: #708090;
  font-family: Calibri;
  background-color: #ffffff;
}
pre {
  color: #708090;
  background-color: #F8F8FF;
}
h1.title {
  color: #0e2d4d;
  font-family: Calibri;
}
h4.date {
  color: #708090;  
  font-family: Calibri;
}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.align = 'center', echo = TRUE)
```

```{r data, include = FALSE}
library(readr)
library(dplyr)
library(ggplot2)
library(knitr)
#install.packages('devtools')
#install.packages('ggthemr')
#install_github('Mikata-Project/ggthemr')
library(ggthemr)

investment_annual_summary <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/d0251f26117bbcf0ea96ac276555b9003f4f7372/investment_annual_summary.csv")
investment_region_summary <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/52f5414f6504e0503e86eb1043afa9b3d157fab2/investment_region_summary.csv")
investment_services_projects <- read_csv("https://assets.datacamp.com/production/repositories/5756/datasets/bcb2e39ecbe521f4b414a21e35f7b8b5c50aec64/investment_services_projects.csv")
```


## Datasets 
### Investment Annual Summary
The `investment_annual_summary` dataset provides a summary of the dollars in millions provided to each of the following regions for each fiscal year, from 2012 to 2018:

1. East Asia and the Pacific      
2. Europe and Central Asia        
3. Latin America and the Caribbean
4. Middle East and North Africa   
5. South Asia                     
6. Sub-Saharan Africa

```{r investment-annual-summary, out.width = '65%', fig.cap = 'Figure 1.1 The Investment Annual Summary for each region for 2012 to 2018.'}
ggthemr('flat dark')
ggplot(investment_annual_summary, aes(x = fiscal_year, y = dollars_in_millions, color = region)) +
  geom_line() +
  scale_colour_ggthemr_d() +
  labs(
    title = "Investment Annual Summary",
    x = "Fiscal Year",
    y = "Dollars in Millions"
  )
```

```{r tables}
#to create table
kable(investment_region_summary, col.names = c("Region", "Dollars in Millions"), align = "cc", caption = "Table 1.1 The total investment summary for each region for the 2012 to 2018 fiscal years.")
```

### Investment Projects in `r params$country`
The `investment_services_projects` dataset provides information about each investment project from 2012 to 2018. Information listed includes the project name, company name, sector, project status, and investment amounts.

```{r brazil-investment-projects, out.width = '65%', fig.cap = 'Figure 1.2 The Investment Services Projects in Brazil from 2012 to 2018.', warning = FALSE}
brazil_investment_projects <- investment_services_projects %>%
  filter(country == params$country) 

ggplot(brazil_investment_projects, aes(x = date_disclosed, y = total_investment, color = status)) +
  geom_point() +
  scale_colour_ggthemr_d() +
  labs(
    title = "Investment Services Projects in Brazil",
    x = "Date Disclosed",
    y = "Total IFC Investment in Dollars in Millions"
  )
```

### Investment Projects in `r params$country` in `r params$fy`
The `investment_services_projects` dataset was filtered below to focus on information about each investment project from the 2018 fiscal year, and is referred to as `brazil_investment_projects_2018`. 

```{r brazil-investment-projects-2018, out.width = '95%', fig.cap = 'Figure 1.3 The Investment Services Projects in Brazil in 2018.', warning = FALSE}
brazil_investment_projects_2018 <- investment_services_projects %>%
  filter(country == params$country,
         date_disclosed >= params$year_start,
         date_disclosed <= params$year_end) 

ggplot(brazil_investment_projects_2018, aes(x = date_disclosed, y = total_investment, color = status)) +
  geom_point() +
  scale_colour_ggthemr_d() +
  labs(
    title = "Investment Services Projects in Brazil in 2018",
    x = "Date Disclosed",
    y = "Total IFC Investment in Dollars in Millions"
  ) 
```


