---
title: "Visualization"
author: "Muhammad Ichsan"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    code_folding : hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    number_sections: true
params:
  country: Brazil
  year_start: 2017-07-01
  year_end: 2018-06-30
  fy: 2018    
---
<style>
#TOC {
  color: #708090;
  font-family: Calibri;
  font-size: 16px; 
  border-color: #708090;
}
body {
  color: #708090;
  font-family: Calibri;
  background-color: #ffffff;
}
pre {
  color: #708090;
  background-color: #F8F8FF;
}
h1.title {
  color: #0e2d4d;
  font-family: Calibri;
}
h4.date {
  color: #708090;  
  font-family: Calibri;
}
</style>

```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.align = 'center', echo = TRUE)
```

# Load Data

We will see the structure of data
```{r data, message=FALSE, warning = FALSE}
#library(readr)
#library(dplyr)
#library(ggplot2)
library(knitr)
#install.packages('devtools')
#install.packages('ggthemr')
#install_github('Mikata-Project/ggthemr')
library(ggthemr)
library(tidyverse)
library(waffle)
#install.packages("Hmisc")
library(Hmisc)
#install.packages("openair")
library(openair)
#install.packages("lattice")
library(lattice)
#library(openair)
library(RColorBrewer)

who_disease <- read_csv("https://assets.datacamp.com/production/repositories/1864/datasets/71386124a72f58a50fbc07b8254f47ef9a867ebe/who_disease.csv")

head(who_disease,10)
```

And then, lets see summary statistics from the data
```{r stat_summary}
summary(who_disease)
```

# Create Visualization

## Pie Chart
```{r pie_chart, message = FALSE, warning = FALSE,out.width = '65%'}
# Wrangle data into form we want. 
disease_counts <- who_disease %>%
    mutate(disease = ifelse(disease %in% c('measles', 'mumps'), disease, 'other')) %>%
    group_by(disease) %>%
    summarise(total_cases = sum(cases))

ggplot(disease_counts, aes(x = 1, y = total_cases, fill = disease)) +
	# Use a column geometry.
	geom_col() +
	# Change coordinate system to polar and set theta to 'y'.
	coord_polar(theta = "y") +
# Clean up the background with theme_void and give it a proper title with ggtitle.
	theme_void() +
	ggtitle('Proportion of diseases')
```

## Waffle Chart
```{r waffle-chart, message = FALSE,out.width = '65%'}
#install.packages("waffle")
#library(waffle)

disease_counts <- who_disease %>%
	group_by(disease) %>%
	summarise(total_cases = sum(cases)) %>% 
	mutate(percent = round(total_cases/sum(total_cases)*100))

# Create an array of rounded percentages for diseases.
case_counts <- disease_counts$percent
# Name the percentage array
names(case_counts) <- disease_counts$disease

# Pass case_counts vector to the waffle function to plot
waffle(case_counts)
```

## Basic Barchart 100% stacked
```{r bar-chart, message = FALSE,out.width = '65%'}
disease_counts <- who_disease %>%
	mutate(
		disease = ifelse(disease %in% c('measles', 'mumps'), disease, 'other') %>% 
		factor(levels = c('measles', 'other', 'mumps')) # change factor levels to desired ordering
	) %>%
	group_by(disease, year) %>%
	summarise(total_cases = sum(cases)) 

# plot
ggplot(disease_counts, aes(x = year, y = total_cases, fill = disease)) +
	geom_col(position = 'fill')
```

## Barchart with Categorical x-axis
```{r bar-chart-categorical, message = FALSE,out.width = '65%'}
disease_counts <- who_disease %>%
	# Filter to on or later than 1999
	filter(year >= 1999) %>% 
	mutate(disease = ifelse(disease %in% c('measles', 'mumps'), disease, 'other')) %>%
	group_by(disease, region) %>%    # Add region to grouping
	summarise(total_cases = sum(cases))

# Set aesthetics so disease is the stacking variable, region is the x-axis and counts are the y
ggplot(disease_counts, aes(x = region, y = total_cases, fill = disease)) +
	# Add a column geometry with the proper position value. 
	geom_col(position = 'fill')

```

## Basic barchart - geom_col
```{r geom-col, message = FALSE,out.width = '65%'}
who_disease %>% 
	# filter to india in 1980
	filter(country == "India", year == 1980) %>% 
	# map x aesthetic to disease and y to cases
	ggplot(aes(x = disease, y = cases)) +
	# use geom_col to draw
	geom_col()
```

## Basic barchart - geom_bar
```{r geom-bar, message = FALSE,out.width = '65%'}
who_disease %>%
	# filter data to observations of greater than 1,000 cases
	filter(cases > 1000) %>%
	# map the x-axis to the region column
	ggplot(aes(x = region)) +
	# add a geom_bar call
	geom_bar()
```

## Point Chart
```{r point-chart, message = FALSE,out.width = '65%'}
interestingCountries <- c("NGA","SDN","FRA","NPL","MYS","TZA","YEM","UKR","BGD","VNM")
who_subset <- who_disease %>% 
	filter(
		countryCode %in% interestingCountries,
		disease == 'measles',
		year %in% c(1992, 2002) # Modify years to 1992 and 2002
	) %>% 
	mutate(year = paste0('cases_', year)) %>% 
	spread(year, cases)
 
# Reorder y axis and change the cases year to 1992
ggplot(who_subset, aes(x = log10(cases_1992), y = reorder(country, cases_1992))) +
	geom_point()
```

## Facet Point Chart with vline
```{r facet point, message = FALSE,out.width = '65%'}
who_subset %>% 
  # calculate the log fold change between 2002 and 1992
	mutate(logFoldChange = log2(cases_2002/cases_1992)) %>% 
	ggplot(aes(x = logFoldChange, y = reorder(country, logFoldChange))) +
	geom_point() +
	geom_vline(xintercept = 0) + 
	xlim(-6,6) +
	# add facet_grid arranged in the column direction by region and free_y scales
	facet_grid(region~., scales = 'free_y')
```

## Flip the axis
```{r flip the axis, message = FALSE,out.width = '65%'}
amr_pertussis <- who_disease %>% 
	filter(   # filter data to our desired subset
		region == 'AMR', 
		year == 1980, 
		disease == 'pertussis',
		cases > 0
	)

## geom_col
# Set x axis as country ordered with respect to cases. 
ggplot(amr_pertussis, aes(x = reorder(country, cases), y = cases)) +
	geom_col() +
	# flip axes
	coord_flip() +
  theme(
	# get rid of the 'major' y grid lines
	panel.grid.major.y = element_blank()
	)

## geom_point
ggplot(amr_pertussis,aes(x = reorder(country, cases), y = cases)) + 
	# switch geometry to point and set size = 2
	geom_point(size = 2) + 
	# change y-axis to log10. 
	scale_y_log10() + 
	# add theme_minimal()
	theme_minimal() +
	coord_flip()
```

## Faceting Geom boxplot
This is just the code,soon will change the data
```{r facet-geom-boxplot}
# remove color filter
# md_speeding %>% 
#    ggplot(aes(x = gender, y = speed)) + 
#    geom_jitter(alpha = 0.3, color = 'steelblue') +
#    geom_boxplot(alpha = 0) +
    # add a facet_wrap by vehicle_color
#    facet_wrap(~vehicle_color) +
    # change title to reflect new faceting
#    labs(title = 'Speed of different car colors, separated by gender of driver')
```

## Create geom_density_ridge
This is just the code,soon will change the data
```{r geom-denstity-ridge}
# md_speeding %>% 
#    mutate(day_of_week = factor(day_of_week, levels = c("Mon","Tues","Wed","Thu","Fri","Sat","Sun") )) # %>% 
#    ggplot(aes( x = percentage_over_limit, y = day_of_week)) + 
#    geom_point(
#        alpha = 0.2,  # make semi-transparent with alpha = 0.2
#        shape = '|',  # turn points to vertical lines with shape = '|'
#        position = position_nudge(y = -0.05) # nudge the points downward by 0.05
#    ) +
#    geom_density_ridges(bandwidth = 3.5, alpha = 0.7) +
#    scale_x_continuous(limits = c(0,150), expand  = c(0,0)) +
#    labs(subtitle = 'Guassian kernel SD = 3.5') +
#    theme( axis.ticks.y = element_blank() )
```

## Create stat-smooth
```{r , out.width = '65%'}
# Amend the plot
ggplot(mtcars, aes(x = wt, y = mpg, color = as.factor(cyl))) +
  geom_point() +
  # Map color to dummy variable "All"
  stat_smooth(se = FALSE, aes(color = "All")) +
  stat_smooth(method = "lm", se = FALSE)
```

## Create Dynamite Plot
```{r dynamite-plor, warning = FALSE}
# Plot wt vs. fcyl
ggplot(mtcars, aes(x = as.factor(cyl), y = wt)) +
  # Add a bar summary stat of means, colored skyblue
  stat_summary(fun.y = mean, geom = "bar", fill = "skyblue") +
  # Add an errorbar summary stat std deviation limits
  stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), geom = "errorbar", width = 0.1)
```

## Dynamite Plot Dodging position
```{r}
# Define a dodge position object with width 0.9
posn_d <- position_dodge(width = 0.9)

# For each summary stat, update the position to posn_d
ggplot(mtcars, aes(x = as.factor(cyl), y = wt, color = as.factor(am), fill = as.factor(am))) +
  stat_summary(fun.y = mean, geom = "bar", position = posn_d, alpha = 0.5) +
  stat_summary(fun.data = mean_sdl, fun.args = list(mult = 1), width = 0.1, position = posn_d, geom = "errorbar")
```

## Create Heat Map
```{r heat-map}
# A palette of 9 reds
red_brewer_palette <- brewer.pal(9, "Reds")

# Update the plot
ggplot(barley, aes(x = year, y = variety, fill = yield)) +
  geom_tile() + 
  facet_wrap(facets = vars(site), ncol = 1) +
  # Update scale to use n-colors from red_brewer_palette
  scale_fill_gradientn(colors = red_brewer_palette)
```

## Wind rose plot
```{r}
# Convert to polar coordinates:
ggplot(mydata, aes(wd, fill = ws)) +
  geom_bar(width = 1) +
  coord_polar(start = -pi/16)
```

## dual axis
```{r, dual-axis}
## From previous step
#y_breaks <- c(59, 68, 77, 86, 95, 104)
#y_labels <- (y_breaks - 32) * 5 / 9
#secondary_y_axis <- sec_axis(
#  trans = identity,
#  name = "Celsius",
#  breaks = y_breaks,
#  labels = y_labels
#)

## Update the plot
#ggplot(airquality, aes(day, Temp)) +
#  geom_line() +
  # Add the secondary y-axis 
#  scale_y_continuous(sec.axis = secondary_y_axis) +
#  labs(x = "Date (1973)", y = "Fahrenheit")
```
















