---
title: "Working with Data in Tidyverse"
author: "Ichsan"
date: "`r format(Sys.time(), '%d %B %Y')`"
output: 
  html_document:
    code_folding : hide
    toc: true
    toc_float:
      collapsed: false
      smooth_scroll: true
    toc_depth: 3
    number_sections: true
---

<style>
#TOC {
  color: #708090;
  font-family: Calibri;
  font-size: 16px; 
  border-color: #708090;
}
body {
  color: #708090;
  font-family: Calibri;
  background-color: #ffffff;
}
pre {
  color: #708090;
  background-color: #F8F8FF;
}
h1.title {
  color: #0e2d4d;
  font-family: Calibri;
}
h4.date {
  color: #708090;  
  font-family: Calibri;
}
</style>


```{r setup, include = FALSE}
knitr::opts_chunk$set(fig.align = 'center', echo = TRUE)
```

```{r load package, message = FALSE, warning = FALSE}
library(tidyverse)
library(skimr)
library(janitor)
```

# Step One

## Read Data
```{r data, warning = FALSE, message = FALSE}
# Create bakeoff but skip first row
bakeoff <- read_csv("https://assets.datacamp.com/production/repositories/1613/datasets/53cf6583aa659942b787897319a1ac053cbcfa5a/bakeoff.csv")

# Print bakeoff
head(bakeoff,10)

# See the structure
glimpse(bakeoff)
```

## Assign missing value
```{r missing-value}
# Filter rows where showstopper is UNKNOWN 
bakeoff %>%
  filter(showstopper == "UNKNOWN")

# Edit to add list of missing values
bakeoff_ <- read_csv("https://assets.datacamp.com/production/repositories/1613/datasets/53cf6583aa659942b787897319a1ac053cbcfa5a/bakeoff.csv", 
                    na = c("", "NA", "UNKNOWN"))

# Filter rows where showstopper is NA 
bakeoff_ %>% filter(is.na(showstopper))
```

## Summarize the data
```{r summarize-data}
bakeoff_ %>% 
  filter(!is.na(us_season)) %>% 
  group_by(us_season)  %>% 
  skim()
```

## Count and Distint
```{r count-distinct}
# Count rows for each result
bakeoff_ %>% 
  distinct(result) 
bakeoff_ %>%
  count(result, sort=TRUE) %>%
  knitr::kable(align = "lc")
```

## Plot Counts
```{r plot-count}
ggplot(bakeoff, aes(episode)) + 
    geom_bar() + 
    facet_wrap(~series)
```

# Tame your data

## Cast column
```{r cast-to-factor}
# Cast result a factor
desserts <- read_csv("desserts.csv", 
                     na = c("", "NA", "N/A"),
                     col_types = cols(
                       uk_airdate = col_date(format = "%d %B %Y"), #cast to date
                       technical = col_number(), #cast to number                       
                       result = col_factor(levels = NULL) #cast to factor
                     )
                    )

# View parsing problems
problems(desserts)

# Glimpse to view
glimpse(desserts)

desserts %>% 
	arrange(desc(uk_airdate))
```

## Recode column character
```{r recode-character}
# Count rows grouping by nut variable
desserts %>% 
    count(signature_nut, sort = TRUE)
    
# Recode filberts as hazelnuts
desserts_2 <- desserts %>% 
  mutate(nut = recode(signature_nut, "filbert" = "hazelnut"))

# Count rows again
desserts_2 %>% 
    count(nut, sort = TRUE)
```

## Recode column numeric
```{r recode-numeric}
# Edit to recode tech_win as factor
desserts <- desserts %>% 
  mutate(tech_win = recode_factor(technical, `1` = 1,
                           .default = 0))

# Count to compare values                      
desserts %>% 
  count(technical == 1, tech_win)
```

## Recode factor to plot
```{r message=FALSE}
# Load data ratings
ratings <- read_csv("02.03_messy_ratings.csv")

# Recode channel as factor: bbc (1) or not (0)
ratings <- ratings %>% 
  mutate(bbc = recode_factor(channel, 
                             "Channel 4" = 0,
                             .default = 1))

ratings$viewer_growth <- c(2.89,2.85,5.00,3.43,2.32,0.58, 1.7, 2.9)
                            
# Select to look at variables to plot next
ratings %>% 
  select(series, channel, bbc, viewer_growth)
  
# Make a filled bar chart
ggplot(ratings, aes(x = series, y = viewer_growth, fill = bbc)) +
  geom_col()
```

## Select and reorder variable
```{r}
# Move channel to front and drop 7-/28-day episode ratings
ratings %>% 
  select(channel, everything(), -ends_with("day"))
```

## Reformat column name
```{r}
ratings_ <- ratings %>%  
  clean_names("snake")

# Glimpse cleaned names
glimpse(ratings_)
```

## Rename, reorder, and subset variable
```{r}
# Adapt code to also rename 7-day viewer data
viewers_7day <- ratings_ %>% 
    select(everything(),
        viewers_7day_ = ends_with("7day"),
        -ends_with("28day"))

# Glimpse
glimpse(viewers_7day)
```

# Tidy your data

## Plot untidy data
```{r message=FALSE,warning=FALSE}
ratings_2 <- read_csv("messy_ratings.csv")

# Plot of episode 1 viewers by series
ratings_2 %>% ggplot(aes(x=series,y=e1)) + geom_col()

# Adapt code to plot episode 2 viewers by series
ggplot(ratings_2, aes(x = series, y = e2)) +
    geom_col()
```

## Gather & Plot
```{r}
tidy_ratings <- ratings_2 %>%
    # Gather and convert episode to factor
	gather(key = "episode", value = "viewers_7day", -series, 
           factor_key = TRUE, na.rm = TRUE) %>%
	# Sort in ascending order by series and episode
    arrange(series, episode) %>% 
	# Create new variable using row_number()
    mutate(episode_count = row_number())

# Plot viewers by episode and series
ggplot(tidy_ratings, aes(x = episode_count, 
                y = viewers_7day, 
                fill = series)) +
    geom_col()
```

## Gather & plot non-sequential column
```{r}
messy_ratings <- read.csv("messy_ratings2.csv")

week_ratings <- messy_ratings  %>% 
	# Select 7-day viewer ratings
    select(series, ends_with("7day")) %>% 
	# Gather 7-day viewers by episode
    gather(episode, viewers_7day, ends_with("7day"), na.rm = TRUE, factor_key = TRUE)
    
# Plot 7-day viewers by episode and series
ggplot(week_ratings, aes(x = episode, 
                y = viewers_7day, 
                group = series)) +
    geom_line() +
    facet_wrap(~series)
```

## Separate a column
```{r}
# Create week_ratings
week_ratings <- messy_ratings %>% 
    select(series, ends_with("7day")) %>% 
    gather(episode, viewers_7day, ends_with("7day"), 
           na.rm = TRUE) %>% 
    separate(episode, into = "episode", extra = "drop") %>% 
    mutate(episode = parse_number(episode))
    
# Edit your code to color by series and add a theme
ggplot(week_ratings, aes(x = episode, y = viewers_7day, 
                         group = series, color = series)) +
    geom_line() +
    facet_wrap(~series) +
    guides(color = FALSE) +
    theme_minimal()
```

## Unite column
```{r}
ratings2 <- tibble(
  series = c(1, 1, 1, 1, 1, 1, 2, 2, 2, 2, 2, 2, 2, 2, 3, 3, 3, 3, 3, 3, 
3, 3, 3, 3, 4, 4, 4, 4, 4, 4, 4, 4, 4, 4, 5, 5, 5, 5, 5, 5, 5, 
5, 5, 5, 6, 6, 6, 6, 6, 6, 6, 6, 6, 6, 7, 7, 7, 7, 7, 7, 7, 7, 
7, 7, 8, 8, 8, 8, 8, 8, 8, 8, 8, 8),
  episode = c(1, 2, 3, 4, 5, 6, 1, 2, 3, 4, 5, 6, 7, 8, 1, 2, 3, 4, 5, 6, 
7, 8, 9, 10, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 1, 2, 3, 4, 5, 6, 
7, 8, 9, 10, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 1, 2, 3, 4, 5, 6, 
7, 8, 9, 10, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10),
  viewers_millions = c(2, 3, 3, 2, 3, 2, 3, 3, 3, 3, 3, 4, 4, 5, 3, 4, 4, 4, 4, 4, 
5, 5, 5, 6, 6, 6, 7, 6, 6, 7, 7, 7, 7, 9, 8, 8, 9, 10, 9, 10, 
10, 9, 10, 13, 11, 11, 12, 12, 12, 12, 12, 11, 12, 15, 13, 13, 
13, 13, 13, 13, 13, 13, 13, 15, 9, 9, 8, 8, 8, 8, 9, 8, 9, 10),
  viewers_decimal = c(".24", "", "", ".6", ".03", ".75", ".1", ".53", ".82", ".6", 
".83", ".25", ".42", ".06", ".85", ".6", ".53", ".71", ".61", 
".82", ".1", ".35", ".7", ".74", ".6", ".65", ".17", ".82", ".95", 
".32", ".76", ".41", ".41", ".45", ".51", ".79", ".28", ".25", 
".95", ".13", ".28", ".02", ".67", ".51", ".62", ".59", ".01", 
".36", ".39", "", ".35", ".09", ".65", ".05", ".58", ".45", ".01", 
".29", ".12", ".13", ".45", ".26", ".44", ".9", ".46", ".23", 
".68", ".55", ".61", ".61", ".01", ".95", ".03", ".04")
)

ratings3 <- ratings2  %>% 
	# Unite and change the separator
	unite(viewers_7day, viewers_millions, viewers_decimal, sep = "") %>%
	# Adapt to cast viewers as a number
	mutate(viewers_7day = as.numeric(viewers_7day))

# Print to view
ratings3
```

## Spread Row to column
```{r}
# Create tidy data with 7- and 28-day viewers
tidy_ratings_all <- messy_ratings %>% 
    gather(episode, viewers, ends_with("day"), na.rm = TRUE) %>% 
    separate(episode, into = c("episode", "days")) %>%  
    mutate(episode = parse_number(episode),
           days = parse_number(days)) 

tidy_ratings_all %>% 
	# Count viewers by series and days
    count(series, days, wt = viewers) %>%
	# Adapt to spread counted values
    spread(days, n, sep = "_")
```

## Masterclass Tidy
```{r}
# Fill in blanks to get premiere/finale data
tidy_ratings <- ratings_2 %>%
    gather(episode, viewers, -series, na.rm = TRUE) %>%
    mutate(episode = parse_number(episode)) %>% 
    group_by(series) %>% 
    filter(episode == 1 | episode == max(episode)) %>% 
    ungroup() %>% glimpse()
```

```{r}
# Recode first/last episodes
first_last <- tidy_ratings %>% 
  mutate(episode = recode(episode, `1` = "first", .default = "last")) 

# Switch the variables mapping x-axis and color
ggplot(first_last, aes(x = series, y = viewers, color = episode )) +
  geom_point() + # keep
  geom_line(aes(group = series)) + # keep
  coord_flip() # keep
```

```{r}
# Calculate relative increase in viewers
bump_by_series <- first_last %>% 
  spread(episode, viewers) %>%   
  mutate(bump = (last - first) / first)
  
# Fill in to make bar chart of bumps by series
ggplot(bump_by_series, aes(x = series, y = bump)) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) # converts to %
```

# Transform Your Data

## Combine two variable
```{r message=FALSE,warning=FALSE}
bakers <- read_csv("baker_results.csv")

head(bakers,10)

glimpse(bakers)

# Create skill variable with 3 levels
bakers_skill <- bakers %>% 
  mutate(skill = case_when(
    star_baker > technical_winner ~ "super_star",
    star_baker < technical_winner ~ "high_tech",
    TRUE ~ "well_rounded"
  ))

head(bakers_skill,10)
  
# Filter zeroes to examine skill variable
bakers_skill %>% 
  filter(star_baker == 0 & technical_winner == 0) %>% 
  count(skill)
```

## Add another bin
```{r}
# Add pipe to drop skill = NA
bakers_skill_ <- bakers %>% 
  mutate(skill = case_when(
    star_baker > technical_winner ~ "super_star",
    star_baker < technical_winner ~ "high_tech",
    star_baker == 0 & technical_winner == 0 ~ NA_character_,
    star_baker == technical_winner  ~ "well_rounded"
  )) %>% 
  drop_na(skill)

head(bakers_skill_,10)

glimpse(bakers_skill_)
  
# Count bakers by skill
count(bakers_skill_,skill)

```

## Cast a factor and examine the levels
```{r}
# Cast skill as a factor
bakers_ <- bakers_skill_ %>% 
  mutate(skill = as.factor(skill),
         series_winner = as.factor(series_winner))

# Examine levels
levels(bakers$skill)

glimpse(bakers_)
```

## Plot factor count
```{r}
# Plot counts of bakers by skill, fill by winner
ggplot(bakers_, aes(x = skill, fill = series_winner)) +
  geom_bar()

# Edit to reverse x-axis order
ggplot(bakers_, aes(x = fct_rev(skill), fill = series_winner)) +
  geom_bar()
```




















